\section{Problem Formulation}
\label{sec:prob}

In this section, we present a pair of dual infinite dimensional linear programs that compute the uncertain backwards reachable set. 
Critically, note that despite the uncertainty being drawn from a distribution at the arrival into each mode, it remains constant throughout that mode. 
As a result, this unknown parameter can be appended to the dynamics of every mode $j$ and treated as a portion of the state-space:
\begin{align}
f_j=\begin{bmatrix}
  \tilde f_j'&\mathbf{0}'_{n_{\theta_j}}
\end{bmatrix}'.
\end{align}
%In this augmented-state-space---henceforth referred to as the state-space of the system---the object of interest still remains the same, $X_{(0,j)},\,\forall j\in \mathcal J$. Furthermore, as the system transitions out of a mode, say at time $\tau_k$ the solution reaches $e_{ij}$, the uncertainty in mode $j$ is not related to the \emph{actual} value of the uncertainty in mode $i$ at $\tau_k$; in fact, the dimensions of the uncertain parameters $n_{\theta_j}$ need not equal $n_{\theta_i}$, much less their distributions.

To address this problem, we rely on the notion of occupation measures, first introduced in \cite{Pitman1977}, to transform the hybrid nonlinear dynamics of the system into a set linear dynamics over measures that can more readily be solved.
Occupation measures can be interested as measuring the time a solution spends in a portion of the state-space. 
For instance, suppose the system enters mode $j$ at $\tau_k$ with the states being initialized as $x(\tau_k)=x_0$ and $\theta(\tau_k)=\theta$.
The occupation measure, \mbox{$\mu_j(\cdot\mid \tau_k,x_0,\,\theta)\in \mathcal M(\mathcal T\times D_j\times \Theta_j)$}, is defined as:
\small
\begin{align}
\hspace*{-1mm}\mu_j(A\times B\times C| \tau_k ,x_0,\theta)=\hspace*{-1.25mm}\int\limits_{\cal T} \hspace*{-1.25mm} I_{A\times B\times C}(t,x(t|\tau_k,x_0,\theta),\theta)dt.
\end{align}
\normalsize
Note the follow relation between the Lebesgue measure on $\mathcal T$ and $\mu_j(\cdot\mid \tau_k,x_0,\theta)$ holds for all $v \in C(\mathcal T\times D_j\times \Theta_j)$:
\begin{align}
\ip{\mu_j(\cdot\mid \tau_k,x_0,\theta),v}=\ip{\lambda_t,v(t,x(t\mid \tau_k,x_0,\theta),\theta)},
\label{eq:mu_lambda}
\end{align}
The occupational measure as defined is a conditional measure -- conditioned on the arrival-time and initial values of the states in that mode.
To consider a set of possible arrival-times and initial conditions, we define the \emph{average occupation measure} by integrating the conditional occupation measure against a measure on the set of possible initial conditions of the mode, $\mu_{s_j} \in  M(\mathcal T\times D_j\times \Theta_j)$:
\begin{align}
\mu_j(A\times B\times C)= \hspace*{-5mm}\int\limits_{\mathcal T\times D_j\times \Theta}\hspace*{-5mm}\mu_j(A\times B\times C\mid \tau_k,x_0,\theta)\,d \mu_{s_j}.
\label{eq:mu_avg}
\end{align}
Observe that by definition, the uncertain variables are independent of the states' initial conditions; hence $\mu_{s_i}\in \mathcal M(\mathcal T\times D_j\times \Theta)$ is expressible as a product measure:
\begin{align}
\mu_{s_j}=\bar\mu_{0_j}\otimes \mu_{\theta_j},\
\end{align}
where $\bar \mu_{0_j}\in \mathcal M(\mathcal T\times D_j)$ is a measure describing the set of initial conditions, and $\mu_{\theta_j}\in \mathcal M(\Theta_j)$ is as in the definition of $\mathcal H$.

Similarly, measures on terminals sets, $\mu_{T_j}\in \mathcal M(X_{(T,j)}\times \Theta_j)$:
\begin{align}
\mu_{T_j}(A\times B)= \hspace*{-4mm}\int\limits_{\mathcal T\times X_{(T,j)}\times \Theta}\hspace*{-4mm}I_{A\times B}(x(T\mid \tau_k,x_0,\theta),\theta)\,d\mu_{s_{j}},
\end{align}
and guards, $\mu_{ G_{e}}\in \mathcal M(\mathcal T\times  G_{(j,k)})$:
\begin{align}
\mu_{G_{(j,k)}}(A\times B\times C)=\hspace*{-5mm}\int\limits_{\mathcal T\times G_{(j,k)}}\hspace*{-5mm}I_{A\times B\times C}(t,x(t\mid \tau_k,x_0,\theta),\theta)\,d\mu_{s_{j}}
\end{align}
for all $(j,k) \in {\cal E}$ can be defined. 
The measures $\mu_{ G_{(j,k)}}$ are supported on the guards of mode $j$ and should be interpreted as the hitting times of the guard.
The {\em final measure} in each mode $j$ can be defined as:
\begin{align}
  \mu_{f_j}=\delta_T\otimes \mu_{T_j}+\sum_{k\in\{l\mid (j,l)\in \mathcal E\}}\mu_{ G_{(j,k)}}.
\label{eq:mu_T}
\end{align}

% Given a set of initial conditions $X_{0}$, the dynamics of the system---under appropriate assumptions---defines a bundle of trajectories of the system states. It is of interest to ensure that this bundle terminates in the desired set $X_T$, making $X_0$ a subset of the BRS; stated differently, it is necessary to relate $\{\mu_{s_j}\}_{j\in \mathcal J}$ with $\{\mu_{f_j}\}_{j\in \mathcal J}$ and the dynamics of the system. 
To compute $X_0$, we relate $\{\mu_{s_j}\}_{j\in \mathcal J}$ with $\{\mu_{f_j}\}_{j\in \mathcal J}$ using the dynamics of the system.
As a first step, define linear operators {$\mathcal L_{ f_j}\colon \mathcal C^1(\mathcal T\times D_j\times \Theta_j)\rightarrow \mathcal C(\mathcal T\times D_j\times \Theta_j)$} as:
\begin{align}
      \mathcal L_{f_j}v=\frac{\partial v}{\partial t}+\ip{\nabla_x v,\tilde f_j}
    \label{eq:Lv}
\end{align}
where $v\in \mathcal C^1(\mathcal T\times D_j\times \Theta_j;\R)$ is an arbitrary test function.
Suppose the system transitioned to mode $j$ at \mbox{$t=\tau_{k-1}$} with the state taking value upon reset $x(\tau_{k-1})$ and $\theta$.
The value of $v$, evaluated along the flow of the system and at $t=\tau_{k}$ is computed using the Fundamental Theorem of Calculus:
\begin{align}
\begin{aligned}
    v& \big(\tau_k,x(\tau_{k}\mid x(\tau_{k-1}),\theta_{k-1})\big)=v(\tau_{k-1},x(\tau_{k-1}),\theta_{k-1})\\
    &+\int_{\tau_{k-1}}^{\tau_{k}}\hspace*{-2mm}\mathcal L_{f}v(t,x(t\mid \tau_{k-1},x(\tau_{k-1}),\theta_{k-1}))\,dt.
\end{aligned}
\label{eq:FTC}
\end{align}
Using Eqn.~(\ref{eq:mu_lambda}), Eqn.~(\ref{eq:FTC}) can be re-written as:
\small
\begin{align}
\begin{aligned}
    v\big(\tau_k,&x(\tau_{k}\mid \tau_{k-1},x(\tau_{k-1}),\theta_{k-1})\big)=v(\tau_{k-1},x(\tau_{k-1}),\theta_{k-1})\\
    &+\ip{\mu_j(\cdot\mid \tau_{k-1},x(\tau_{k-1},\theta_{k-1}),\mathcal L_{ f}v},
\end{aligned}
\end{align}
\normalsize
which can be simplified further by using Eqns.~(\ref{eq:mu_avg})--(\ref{eq:mu_T}):
\begin{align}
  \ip{\mu_{f_j},v}=\ip{\mu_{s_j},v}+\ip{\mu_{j},\mathcal L_{f}v}.
  \label{eq:liouville_1}
\end{align}

Alternatively, using the standard definition of adjoint operators\footnote{A linear operator $\mathcal L$ and its adjoint, $\mathcal L'$, satisfy the following relation:
\begin{align*}
    \ip{\mathcal L'\mu,v}=\ip{\mu,\mathcal Lv}.
\end{align*}
% \begin{align*}
%     \ip{\mathcal L'\mu,v}=\ip{\mu,\mathcal Lv}=\int\limits_{\mathcal X}\mathcal Lv\,d\mu.
% \end{align*}
}, Eqn.~(\ref{eq:liouville_1}) is re-written as:
\begin{align}
\ip{\mu_{f_j},v}=\ip{\mu_{s_j},v}+\ip{\mathcal L'_{f}\mu_{j},v}.
  \label{eq:liouville_2}
\end{align}
\emph{Eqn~(\ref{eq:liouville_2}) defines a linear relation that initial and final measures evolving according to the hybrid dynamics must satsify.}


During the execution of a hybrid system, any mode can be entered either at $t=0$ or due to reset.
The initial measure in the $(t,x)$-coordinate can be decomposed as:
\begin{align}
  \bar\mu_{0_j}=\delta_0\otimes\mu_{0_j}+\pi^{(t,x)}_*\sigma_{0_j}
\end{align}
where $\mu_{0_j}\in \mathcal M(D_j)$ is the measure describing initial conditions to the system at $t=0$, $\sigma_{0_j}\in \mathcal M(\mathcal T\times D_j\times \Theta_j)$ is a measure describing initial conditions arriving due to reset, and $\pi^{(t,x)}_*$ denotes the pushforward constructed by lifting the $(t,x)$-projection operator, $\pi^{(t,x)}: \mathcal T\times D_j\times \Theta_j \to \mathcal T\times D_j$, to measures (refer to Chapter 11 in \cite{lee2003smooth} for an introduction to pushforwards). 
State resets occur when the state reaches a guard. 
As a result, we must formalize a relationship between $\mu_{ G_{(i,j)}}$ and $\sigma_{0_j},~\forall (i,j)\in \mathcal E$.
To formalize this relationship notice that $\sigma_{0_j}$ can be decomposed into measures corresponding to the source of each arrival state:
\begin{align}
  \sigma_{0_j}=\sum_{i\in \{k\mid (k,j)\in \mathcal E\}} \sigma_{(i,j)}\otimes \mu_{\theta_j},
\end{align}
where $\sigma_{(i,j)}$ is the measure describing initial conditions that are reset into mode $j$ from guard $G_{(i,j)}$.
Upon reaching the guard, the system transitions according to the reset map, $R_{(i,j)}$, which can be treated as a nonlinear transformation between $D_i$ and $D_j$.
By applying a change of variables formula, as in Lemma 1 in \cite{shia2014convex}, we have:
\begin{align}
    \ip{\sigma_{(i,j)},w}=\ip{\pi^{(t,x)}_*\mu_{ G_{(i,j)}},w\circ R_{(i,j)}}
    \label{eq:reset_measure}
\end{align}
where $w\in \mathcal C(\mathcal T\times \mathcal D_j)$ and
$$
  \ip{\pi_{t,x}\mu_{ G_{(i,j)}},s}=\ip{\mu_{ G_{(i,j)}},s},\,\forall s\in \mathcal C(\mathcal T\times D_i);
$$
essentially, $\sigma_{(i,j)}$ is a push-forward measure of $\mu_{ G_{(i,j)}}$.
%\begin{remark}
%\label{remark:primal}
%  \red{A note on domain in time and the Liouville's equations}
%\end{remark}
  \subsection{The primal}
  \label{ssec:primal}
  With the constraints expressed in terms of measures, the problem of approximating the BRS is formulated as an infinite-dimensional Linear Program that supremizes the \emph{volume} of the set of initial condition.
  \begin{flalign}\nonumber
  &\sup_{\Lambda}\sum_{j=1}^{n_m}\ip{\mu_{0_j},1}&&&(P)\\\nonumber
  &\text{st.}\\
  &\mu_{s_j}+\mathcal L_{f}'\mu_j=\,\mu_{f_j}&&&\forall j\in \N_{n_m}\label{eq:primal:liouville}\\
  &\mu_{0_j}+\hat\mu_{0,j}=\,\lambda_j&&&\forall j\in \N_{n_m}\\
  &\sum_{j=1}^{n_m}\ip{\mu_{T_j},1}=\,\sum_{j=1}^{n_m}\ip{\mu_{0_j},1}\label{eq:mass_conservation}
  \end{flalign}
  where $\lambda_j$ is the Lebesgue measure supported on $D_j$.
  $$\Lambda=\{\mu_j,\mu_{0_j},\mu_{T_j},\hat\mu_{0_j},\mu_{ G_{(j,k)}}\ge 0,\,\forall j\in \mathcal \N_{n_m},(j,k)\in \mathcal E\}.$$
Variables $\hat\mu_{0_j}\in \mathcal M(D_j)$ are slack variables introduced to enforce a stronger constraint than absolute continuity of $\mu_{0_j}$ wrt. to $\lambda_j$
  \begin{flalign}
  &&&\mu_{0_j}(A)\le \lambda_j(A)&\forall A\subset D_j\label{eq:primal:domination}
    \end{flalign}
  The constraint in Eqn.~(\ref{eq:mass_conservation}) ensures that all trajectories that emanate $\cup_{j\in \mathcal J}\,spt(\mu_{0_j})$ reach $X_{T}$ at $t=T$, and is not {\em stuck} at any of the guards.
  %%%%%%%%%%
  \begin{lemma}
   If $\mu_{0_j},\forall j\in \mathcal J$ is part of the optimal solution of ($P$) then $\bigcup_{j\in \mathcal J}\,spt(\mu_{0_j})$ is the BRS of the system. In addition, the optimal value of ($P$) is equal to $\sum_{j\in \mathcal J}\lambda_j(X_{0_j})$, the sum of \emph{volumes} of the BRSs in each mode.
  \end{lemma}

  \begin{proof}
  Suppose $\sum_{j\in \mathcal J}\lambda_j(spt(\mu_{0_j})\backslash X_{(0,j)})>0$, then by Lemma~\ref{lemma:existence}, there exist trajectories that begin in $\cup_{j\in \mathcal J}(spt(\mu_{0_j})\backslash X_{(0,j)})$ that reach $X_T$; this is a contradiction. Thus,
  \begin{align}
  &\bigcup_{j\in \mathcal J} spt(\mu_{0_j})\subset \bigcup_{j\in \mathcal J} X_{(0,j)},\\
  &\sum_{j\in \mathcal J}\lambda_j(spt(\mu_{0_j}))\le\sum_{j\in \mathcal J}\lambda_j( X_{(0,j)}).
  \label{eq:support_lemma:1}
  \end{align}
    By definition of the BRS, all state trajectories that emanate from a subset of $X_0$ end in $X_T$. That is, for each $j\in \mathcal J$ and initial measure $\mu_{0_j}$, if $spt(\mu_{0_j})\subset X_{(0,j)}$, there exist measures $\mu_{j}$ and $\mu_{f_j}$ that satisfy Eqn.~(\ref{eq:primal:liouville}). Thus the following inequality is true.
    \begin{align}
    \sum_{j\in \mathcal J}\lambda_j(spt(\mu_{0_j}))\ge \sum_{j\in \mathcal J}\lambda_j(X_{(0,j)})
      \label{eq:support_lemma:2}
    \end{align}
   From Eqns.~(\ref{eq:support_lemma:1})\&(\ref{eq:support_lemma:2}), $\cup_{j\in \mathcal J}\,spt(\mu_{0_j})$ is the BRS of the system.
    \par
    That the optimal value of $(P)$ is volume of the BRS follows from Eqn.~(\ref{eq:primal:domination}) and the observation that \mbox{$\lambda_{j}|_{X_{(0,j)}},\forall j\in \mathcal J$} is feasible in ($P$).
  \end{proof}

  \subsection{The dual}
  \label{ssec:dual}
    The dual corresponding to $(P)$ is derived using standard techniques and is presented below.
    \par
    \footnotesize
    \begin{flalign}\nonumber
    &&&\inf \sum_{j\in \N_{n_m}}\ip{\lambda_j,w_j}&(D)\\\nonumber
    &&&\text{st.}\\
    &&&w_j\ge \,0&\forall (x,j)\in \mathcal D\\
    &&& v_j(T,\cdot)+q\ge\, 0 ,\> &\forall (x,j,\theta)\in \mathcal X_T\times \Theta \label{eq:dual:terminal}\\
    &&& - \mathcal L_{\tilde f}v_j\ge\,0 ,\> &\forall (t,x,j,\theta)\in \mathcal T\times\mathcal D\times \Theta\label{eq:dual:lfv}\\
    &&& w_j-\ip{\mu_{\theta_j},v(0,\cdot)}-q\ge \,1 ,\> &\forall (x,j)\in \mathcal D\label{eq:dual:levelset}\\
    &&&v_j\ge\, \ip{\mu_{\theta_k},v_k}\circ R_{(j,k)},&\forall (t,x,\theta,(j,k)),\in \mathcal T\times \mathcal G\times \mathcal E\label{eq:dual:mode_transition}
    \end{flalign}
    \normalsize
    where $q\in \R$, $v_j\in C^1(\mathcal T\times \mathrm M_j\times \Theta_j)$ and $w_j\in C(\mathrm M_j)$.
    \begin{lemma}
      If $(w,v,q)$ is the solution to (D), then the super-level set
      \begin{align}
      \bigcup_{j\in \mathcal J}\,\{x\mid w_j(x)\ge 1\}
      \end{align}
      is an outer approximation of the BRS of the system whose dynamics is described by Alg.~\ref{alg:execution}.
    \end{lemma}
    \begin{proof}
    The approach we adopt to prove this lemma is to construct the projection of the BRS on any mode and show that it is a 1-level set of the appropriate function. To assist in constructing the arguments, assume wlog., that the state trajectory terminates in $X_{(T,j_k)}$ for some $j_k$. The state trajectory must have arrived in mode $j_k$ through a finite sequence of mode-transitions (according to Assumption~\ref{assump:zeno}); wlog., let this sequences of mode-transitions be of length $k$. Suppose the states entered mode $j_k$ at time $\tau_k$, then, from the fundamental theorem of calculus and the constraints in Eqns.~(\ref{eq:dual:terminal})\&(\ref{eq:dual:lfv}), the following inequalities follow.
    \begin{align}
      -q\le v_{j_k}(T,x(T\mid x(\tau_k^+),\theta),\theta)\le v_j(\tau_k,x(\tau_k^+),\theta)\\
      \Rightarrow -q\le \ip{\mu_{\theta_{j_k}},v_{j_k}(\tau_k,x(\tau_k^+),\theta)}
    \end{align}
    By iterative application of the constraint in Eqn.~(\ref{eq:dual:mode_transition}) and finally Eqn.~(\ref{eq:dual:levelset}), it follows that
    \begin{align}
      -q\le&\, \ip{\mu_{\theta_{j_k}},v_{j_k}(t,x,\theta)}\circ R_{(j_{k-1},j_{k})}(\tau_{k},x(\tau_{k}^-))\\
      \le&\, v_{j_{k-1}}(\tau_{k},x(\tau_{k}^-\mid x(\tau_{k-1}^+),\theta),\theta)\\
      \le &\, \ip{\mu_{\theta_{j_{k-1}}},v_{j_k}(\tau_k,x(\tau_{k-1}^+),\theta)}\\\nonumber
      &\,\vdots\\
      \le &\,v_{j_0}(\tau_1,x(\tau_1^-\mid x_0,\theta),\theta)\\
      \le &\,v_{j_0}(0,x_0,\theta)\\
      \le &\,\ip{\mu_{\theta_{j_0}},v_{j_0}(0,x_0,\theta)}\\
      \le &\, w_{j_0}(x_0)-q-1.
    \end{align}
    The final inequality implies that for every trajectory that ends in $X_{(t,j_k)}$, $x(t)=x_0\in D_{j}$  satisfies the condition $w_{x_0}\ge 1$. Thus the set of initial conditions that begin in mode $j_0$ and reach the terminal set projected into mode $j_k$ is given by the super-level set
    \begin{align}
      I_{(j_0,j_k)}=\{x\mid w_{j_0}\ge 1\}.
    \end{align}
    Note that the definition of $I_{j_0,j_k}$ does not depend on the mode in which the terminal set is reached; thus \mbox{$I_{(j_0,\mathcal J)}=X_{(0,j_0)}$}. Finally, by observing that $j_0$ is an arbitrary element of $\mathcal J$, we deduce the stated result.
    \end{proof}
    \begin{lemma}
      There is not gap between (P) and (D).
    \end{lemma}
    \begin{proof}
      The proof follows from \cite[Theorem 3.10]{Anderson1987}, and is similar to \cite[Theorem 2]{henrion2014convex}; it is not presented for brevity.
    \end{proof}
    \begin{remark}
    There are two key aspects of the presentation in this section that deserve re-iteration: (1) by definition, the uncertainties that influence the dynamics can be visualized as a discrete random process with updates to the instantiation of the uncertainty occurring upon entering a new mode; (2) the estimated BRS is the set of initial conditions from which {\em all} trajectories that emanate reach the terminal set for {\em all} possible discrete sequence of uncertainty. As a direct implication of the second point, the solution of the problem is the intersection of the BRS of every possible sequence of uncertainty.
    \end{remark}
